---
title: "Clustering Coefficient Analysis"
author: "Samuel Hansen"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)
```

```{r}
# Initialize libraries 
library(GGally)
library(tidyverse)

# Clustering coefficient input files 
# avg_top10_coef_file_in <- "WeightedClusteringCoefficient_MonthlyAverageTop10/weightedClusteringCoefficients.csv"
# avg_coef_file_in <- "WeightedClusteringCoefficient_MonthlyAverage/weightedClusteringCoefficients.csv"
complete_top10_coef_file_in <- "WeightedClusteringCoefficient_CompleteGraphTop10/weightedClusteringCoefficients.csv"
complete_coef_file_in <- "WeightedClusteringCoefficient_CompleteGraph/weightedClusteringCoefficients.csv"

# Node strength input files 
complete_top10_ns_file_in <- "data/complete_top10_ns.tsv"
complete_ns_file_in <- "data/complete_ns.tsv"

# LIWC input file 
liwc_file_in <- "data/liwc_data.tsv"

df <-
  # Read in LIWC data 
  read_tsv(liwc_file_in, col_names = FALSE) %>%
  plyr::rename(replace = c("X1" = "subreddit", "X2" = "category", "X3" = "fraction")) %>%
  spread(category, fraction) %>%
  
  # Impute missing values with column medians 
  dmap_at(colnames(.), ~ifelse(is.na(.x), median(.x, na.rm = T), .x))  %>%
  
  # Merge with complete graph data 
  left_join(read_csv(complete_coef_file_in), by = c("subreddit" = "SubReddit_Name")) %>%
  plyr::rename(replace = c("Clustering_Coefficients" = "complete_clust_coef", 
                           "Log_Clustering_Coefficients" = "complete_log_clust_coef")) %>%
  
  # Merge with complete top 10% graph data 
  left_join(read_csv(complete_top10_coef_file_in), by = c("subreddit" = "SubReddit_Name")) %>%
  plyr::rename(replace = c("Clustering_Coefficients" = "complete_top10_clust_coef", 
                           "Log_Clustering_Coefficients" = "complete_top10_log_clust_coef")) %>%

  # Merge with complete top 10% graph data 
  left_join(read_tsv(complete_ns_file_in)) %>%
  select(-X1) %>%
  plyr::rename(replace = c("node_strength" = "complete_ns")) %>% 
  left_join(read_tsv(complete_top10_ns_file_in)) %>%
  plyr::rename(replace = c("node_strength" = "complete_top10_ns")) %>% 
  select(-X1)
```

#Network Properties vs. Negative Sentiment 

##Complete Graph 
```{r}
my_fn <- function(data, mapping, ...){
  p <- ggplot(data = data, mapping = mapping) + 
    geom_point() + 
    geom_smooth(method=loess, fill="blue", color="blue", ...) 
  p
}
labels <- c("Node Strength", "Clust. Coef.", "Neg. Sent.")
df %>%
  select(complete_ns, complete_clust_coef, negemo) %>%
  ggpairs(mapping = ggplot2::aes(alpha = 20),
          lower = list(continuous = my_fn),
          columnLabels = labels,
          upper = list(continuous = wrap("cor", size = 3)),
          title = "Complete Graph Network Properties vs. Negative Sentiment")
```

##Complete Graph Filtered to Top 10% of Edge Weights
```{r}
df %>%
  select(complete_top10_ns, complete_top10_clust_coef, negemo) %>%
  ggpairs(mapping = ggplot2::aes(alpha = 5),
          lower = list(continuous = my_fn),
          columnLabels = labels,
          upper = list(continuous = wrap("cor", size = 3)),
          title = "Complete Top 10% Graph: Network Properties vs. Negative Sentiment")
```

#Clustering coefficient vs. negative sentiment

##Complete Graph 

We can examine whether a relationship exists between the weighted clustering
coefficient and negative sentiment by examining the following plot and 
inspecting a linear regression analysis. 
```{r}
df %>%
  ggplot(mapping = aes(x = complete_clust_coef, y = negemo)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "loess") +
  labs(x = "Weighted Clustering Coefficient", 
       y = "Negative Emotion Score",
       title = "Complete Graph: \nClustering Coefficient vs. Negative Sentiment") 
```

###Linear Regression: Clusterting Coefficient vs. Negative Sentiment 

```{r}
lm.fit <- lm(negemo ~ complete_clust_coef, data = df)
summary(lm.fit)
```

There appears to be a **no** statistically significant relationship
between clustering coefficient and negative sentiment. 

##Complete Graph Filtered to Top 10% of Edge Weights 

We can examine whether a relationship exists between the weighted clustering
coefficient and negative sentiment by examining the following plot and 
inspecting a linear regression analysis. 
```{r}
df %>%
  ggplot(mapping = aes(x = complete_top10_clust_coef, y = negemo)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "loess") +
  labs(x = "Weighted Clustering Coefficient", 
       y = "Negative Emotion Score",
       title = "Complete Top 10% Graph: \nClustering Coefficient vs. Negative Sentiment") 
```

###Linear Regression: Clusterting Coefficient vs. Negative Sentiment 

```{r}
lm.fit <- lm(negemo ~ complete_top10_clust_coef, data = df)
summary(lm.fit)
```

There is a weak, yet statistically significant negative relationship 
between clustering coefficient and negative sentiment. 

###LOESS Regression: Clusterting Coefficient vs. Negative Sentiment 

```{r}
loess.fit <- loess(negemo ~ complete_top10_clust_coef, data = df)
summary(loess.fit)
```

#What is the distribution of node strength? 

##Complete Reddit Graph 

###Top 20 Subreddits by Node Strength 
```{r}
df %>% 
  arrange(desc(complete_ns)) %>%
  slice(1:20) %>%
  ggplot(mapping = aes(x = reorder(subreddit, complete_ns), y = complete_ns)) +
  geom_bar(stat = "identity") +
  # scale_y_continuous(breaks = seq(0,0.13,0.01), labels = scales::percent) +
  coord_flip() +
  labs(x = "Subreddit", y = "Node Strength",
       title = "Top 20 Subreddits by Node Strength")
```

###Node Strength vs. Negative Sentiment 
```{r}
df %>%
  ggplot(mapping  = aes(x = complete_ns, y = negemo)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "loess") +
  # geom_smooth(method = "lm", color = "red") + 
  labs(x = "Node Strength", y = "Negative Sentiment Score",
       title = "Complete Graph:\nNode Strength vs. Negative Sentiment")
```

###Linear Regression: Node Strength vs. Negative Sentiment 

```{r}
lm.ns.fit <- lm(negemo ~ complete_ns, data = df)
summary(lm.ns.fit)
```


```{r}
# IGNORE THIS CODE FOR NOW 
# df <-
#   df %>%
#   mutate(quartile = ifelse(complete_top10_clust_coef <= 
#                              quantile(complete_top10_clust_coef, prob = .25, na.rm = T),
#                            "bottom_25",
#                            ifelse(complete_top10_clust_coef >= 
#                                     quantile(complete_top10_clust_coef, prob = .75, na.rm = T),
#                                   "top_25", "middle")))
# df %>%
#   filter(quartile != "middle") %>%
#   ggplot(mapping = aes(x = quartile, y = negemo)) +
#   geom_bar(stat = "identity") +
#   labs(x = "Weighted Clustering Coefficient Quartile",
#        y = "Negative Sentiment Score",
#        title = "Negative Sentiment vs. Top & Bottom Clustering Coefficient Quartiles")
```
