---
title: "Clustering Coefficient Analysis"
author: "Samuel Hansen"
output: github_document
---
```{r, warning=FALSE, message=FALSE, echo = FALSE}
# Initialize libraries 
library(tidyverse)

# Initialize input files
# avg_top10_coef_file_in <- "WeightedClusteringCoefficient_MonthlyAverageTop10/weightedClusteringCoefficients.csv"
# avg_coef_file_in <- "WeightedClusteringCoefficient_MonthlyAverage/weightedClusteringCoefficients.csv"
complete_top10_coef_file_in <- "WeightedClusteringCoefficient_CompleteGraphTop10/weightedClusteringCoefficients.csv"
complete_coef_file_in <- "WeightedClusteringCoefficient_CompleteGraph/weightedClusteringCoefficients.csv"
liwc_file_in <- "data/liwc_data.tsv"

df <-
  # Read in LIWC data 
  read_tsv(liwc_file_in, col_names = FALSE) %>%
  plyr::rename(replace = c("X1" = "subreddit", "X2" = "category", "X3" = "fraction")) %>%
  spread(category, fraction) %>%
  
  # Impute missing values with column medians 
  dmap_at(colnames(.), ~ifelse(is.na(.x), median(.x, na.rm = T), .x))  %>%
  
  # Merge with complete graph data 
  left_join(read_csv(complete_coef_file_in), by = c("subreddit" = "SubReddit_Name")) %>%
  plyr::rename(replace = c("Clustering_Coefficients" = "complete_clust_coef", 
                           "Log_Clustering_Coefficients" = "complete_log_clust_coef")) %>%
  
  # Merge with complete top 10% graph data 
  left_join(read_csv(complete_top10_coef_file_in), by = c("subreddit" = "SubReddit_Name")) %>%
  plyr::rename(replace = c("Clustering_Coefficients" = "complete_top10_clust_coef", 
                           "Log_Clustering_Coefficients" = "complete_top10_log_clust_coef"))
```

#What is the relationship between clustering coefficient and negative sentiment? 

##Complete Graph 

We can examine whether a relationship exists between the weighted clustering
coefficient and negative sentiment by examining the following plot and 
inspecting a linear regression analysis. 
```{r}
df %>%
  ggplot(mapping = aes(x = complete_clust_coef, y = posemo)) +
  geom_point() +
  geom_smooth(method = "loess") +
  labs(x = "Weighted Clustering Coefficient", 
       y = "Negative Emotion Score",
       title = "Complete Graph: \nClustering Coefficient vs. Negative Sentiment") 
```

```{r}
lm.fit <- lm(negemo ~ complete_clust_coef, data = df)
summary(lm.fit)
```

There appears to be a **no** statistically significant relationship
between clustering coefficient and negative sentiment. 

##Complete Graph Filtered to Top 10% of Edge Weights 

We can examine whether a relationship exists between the weighted clustering
coefficient and negative sentiment by examining the following plot and 
inspecting a linear regression analysis. 
```{r}
df %>%
  ggplot(mapping = aes(x = complete_top10_clust_coef, y = posemo)) +
  geom_point() +
  geom_smooth(method = "loess") +
  labs(x = "Weighted Clustering Coefficient", 
       y = "Negative Emotion Score",
       title = "Complete Top 10% Graph: \nClustering Coefficient vs. Negative Sentiment") 
```

```{r}
lm.fit <- lm(negemo ~ complete_top10_clust_coef, data = df)
summary(lm.fit)
```

There appears to be a weak, yet statistically significant relationship
between clustering coefficient and negative sentiment. 

```{r}
# IGNORE THIS CODE FOR NOW 
# df <-
#   df %>%
#   mutate(quartile = ifelse(clust_coef <= quantile(clust_coef, prob = .25, na.rm = T), 
#                            "bottom_25",
#                            ifelse(clust_coef >= quantile(clust_coef, prob = .75, na.rm = T), 
#                                   "top_25", "middle")))
# df %>%
#   filter(quartile != "middle") %>%
#   ggplot(mapping = aes(x = quartile, y = negemo)) +
#   geom_bar(stat = "identity") +
#   labs(x = "Weighted Clustering Coefficient Quartile",
#        y = "Negative Sentiment Score",
#        title = "Negative Sentiment vs. Top & Bottom Clustering Coefficient Quartiles")
```
