---
title: "Clustering Coefficient Comparison"
author: "Samuel Hansen"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)
```

```{r}
# Initialize libraries 
library(stringr)
library(tidyverse)

# NOTE: I only use data from the graphs filtered to the Top 10% of edge weights.
# "Monthly" refers to the graph built from monthly averages, and "yearly"
# refers to the graph built from user overlaps over the year. 

# Clustering coefficient input files 
monthly_coef_file_in <- "WeightedClusteringCoefficient_MonthlyAverageTop10/weightedClusteringCoefficients.csv"
yearly_coef_file_in <- "WeightedClusteringCoefficient_CompleteGraphTop10/weightedClusteringCoefficients.csv"

# Alternate clustering coefficient input files
monthly_alt_clust_coef_file_in <- "data/weighted-coefficients-reddit-monthly-average-top10.csv"
yearly_alt_clust_coef_file_in <- "data/weighted-coefficients-reddit-top10.csv"

# Node strength input files 
yearly_ns_file_in <- "data/complete_top10_ns.tsv"
monthly_ns_file_in <- "data/monthly_top10_ns.tsv"

# LIWC input file 
liwc_file_in <- "data/liwc_data.tsv"

df <-
  # Read in LIWC data 
  read_tsv(liwc_file_in, col_names = FALSE) %>%
  plyr::rename(replace = c("X1" = "subreddit", "X2" = "category", "X3" = "fraction")) %>%
  spread(category, fraction) %>%
  
  # Impute missing values with column medians 
  dmap_at(colnames(.), ~ifelse(is.na(.x), median(.x, na.rm = T), .x))  %>%
  
  # Merge with yearly graph data clustering coefficients 
  left_join(read_csv(yearly_coef_file_in), by = c("subreddit" = "SubReddit_Name")) %>%
  plyr::rename(replace = c("Clustering_Coefficients" = "yearly_clust_coef", 
                           "Log_Clustering_Coefficients" = "yearly_log_clust_coef")) %>%
  
  # Merge with monthly graph data clustering coefficients 
  left_join(read_csv(monthly_coef_file_in), by = c("subreddit" = "SubReddit_Name")) %>%
  plyr::rename(replace = c("Clustering_Coefficients" = "monthly_clust_coef", 
                           "Log_Clustering_Coefficients" = "monthly_log_clust_coef")) %>%
  
  # Merge with yearly graph data alternate clustering coefficients 
  left_join(read_csv(yearly_alt_clust_coef_file_in), by = c("subreddit" = "SubReddit_Name")) %>%
  plyr::rename(replace = c("Clustering_Coefficients" = "yearly_alt_clust_coef")) %>%
  
  # Merge with monthly graph data alternate clustering coefficients 
  left_join(read_csv(monthly_alt_clust_coef_file_in), by = c("subreddit" = "SubReddit_Name")) %>%
  plyr::rename(replace = c("Clustering_Coefficients" = "monthly_alt_clust_coef")) %>%
  
  # Merge with node strength data
  left_join(read_tsv(yearly_ns_file_in)) %>%
  plyr::rename(replace = c("node_strength" = "yearly_ns")) %>% 
  select(-X1) %>%
  left_join(read_tsv(monthly_ns_file_in)) %>%
  plyr::rename(replace = c("node_strength" = "monthly_ns")) %>% 
  select(-X1)
```


# Clustering Coefficient vs. Negative Sentiment by Graph Type

##Scatterplots 
```{r}
df %>%
  select(negemo, monthly_clust_coef, yearly_clust_coef, 
         monthly_alt_clust_coef, yearly_alt_clust_coef) %>%
  gather(clust_coef_type, clust_coef, monthly_clust_coef:yearly_alt_clust_coef) %>%
  mutate(graph = ifelse(str_detect(clust_coef_type, "monthly"), "Monthly Graph", "Yearly Graph"),
         clust_coef_type = ifelse(str_detect(clust_coef_type, "alt"), 
                                  "Onnela Coefficient", "Barrat Coefficient")) %>%
  ggplot(mapping = aes(x = clust_coef, y = negemo)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = "loess") +
  facet_grid(graph~clust_coef_type, scales = "free_x") +
  labs(x = "Clustering Coefficient Value", y = "Negative Sentiment Score",
       title = "Clustering Coefficient vs. Negative Sentiment by Graph Type")
```

##Barplots 
```{r}
clust_summary_df <-
  df %>%
  select(negemo, monthly_clust_coef, yearly_clust_coef, 
         monthly_alt_clust_coef, yearly_alt_clust_coef) %>%
  gather(clust_coef_type, clust_coef, monthly_clust_coef:yearly_alt_clust_coef) %>%
  mutate(graph = ifelse(str_detect(clust_coef_type, "monthly"), "Monthly Graph", "Yearly Graph"),
         clust_coef_type = ifelse(str_detect(clust_coef_type, "alt"), 
                                  "Onnela Coefficient", "Barrat Coefficient")) %>%
  
  group_by(clust_coef_type, graph) %>%
  mutate(quartile = ifelse(clust_coef >= quantile(clust_coef, prob = 0.75, na.rm = T), "Top 25%",
                           ifelse(clust_coef <=  quantile(clust_coef, prob = 0.25, na.rm = T), "Bottom 25%",
                           "middle"))) %>%
  filter(quartile != "middle") 
```

```{r}
label.df <- data.frame(clust_coef_type = "Onnela Coefficient",
                       graph = c("Monthly Graph", "Yearly Graph"),
                       quartile = "Top 25%",
                       mean_negemo = c(0.0193, 0.0195))
clust_summary_df %>%
  group_by(graph, clust_coef_type, quartile) %>%
  summarize(mean_negemo = mean(negemo),
            se = sd(negemo)/sqrt(n())) %>%
  mutate(ymin = mean_negemo - se,
         ymax = mean_negemo + se) %>%
  ggplot(mapping = aes(x = quartile, y = mean_negemo, fill = quartile)) +
  geom_bar(stat = "identity") +
  geom_errorbar(mapping = aes(ymax = ymax, ymin = ymin)) +
  facet_grid(graph~clust_coef_type) +
  labs(x = "Clustering Coefficient Quartile", y = "Mean Negative Sentiment Score",
       title = "Clustering Coefficient vs. Negative Sentiment by Graph Type") +
  geom_text(data = label.df, label = c("*", "**")) +
  guides(fill=FALSE)
```

##Mann-Whitney Tests 

###Negative Sentiment vs. Onnela Coefficient 

####Monthly Graph
```{r}
clust_summary_df %>%
  filter(clust_coef_type == "Onnela Coefficient", 
         graph == "Monthly Graph") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(negemo, quartile) %>%
  as.matrix() %>%
  wilcox.test(negemo ~ quartile, data = .) 
```

####Yearly Graph
```{r}
clust_summary_df %>%
  filter(clust_coef_type == "Onnela Coefficient", 
         graph == "Yearly Graph") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(negemo, quartile) %>%
  as.matrix() %>%
  wilcox.test(negemo ~ quartile, data = .) 
```

###Negative Sentiment vs. Barrat Coefficient 

####Monthly Graph
```{r}
clust_summary_df %>%
  filter(clust_coef_type == "Barrat Coefficient", 
         graph == "Monthly Graph") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(negemo, quartile) %>%
  as.matrix() %>%
  wilcox.test(negemo ~ quartile, data = .) 
```

####Yearly Graph
```{r}
clust_summary_df %>%
  filter(clust_coef_type == "Barrat Coefficient", 
         graph == "Yearly Graph") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(negemo, quartile) %>%
  as.matrix() %>%
  wilcox.test(negemo ~ quartile, data = .) 
```

#Node Strength vs. Negative Sentiment 

##Scatterplots
```{r}
ns_summary_df <- 
  df %>%
  select(posemo, negemo, yearly_ns, monthly_ns) %>%
  gather(graph, node_strength, yearly_ns:monthly_ns) %>%
  mutate(graph = str_replace(graph, pattern = "_ns", replacement = ""),
         graph = ifelse(graph == "yearly", "Yearly Graph", "Monthly Graph")) %>%
  gather(sentiment, score, posemo:negemo) %>%
  group_by(graph, sentiment) %>%
  mutate(quartile = ifelse(node_strength >= quantile(node_strength, prob = 0.75, na.rm = T), 
                           "Top 25%",
                         ifelse(node_strength <=  quantile(node_strength, prob = 0.25, na.rm = T), 
                                "Bottom 25%", "middle")))
```

```{r}
sent_labs = c("posemo" = "Positive Sentiment",
              "negemo" = "Negative Sentiment")
ns_summary_df %>%
  ggplot(mapping = aes(x = node_strength, y = score)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "loess") +
  facet_grid(graph~sentiment, labeller = labeller(sentiment = sent_labs)) +
  labs(x = "Node Strength", y = "Sentiment Score", 
       title = "Node Strength vs. Sentiment by Graph Type")
```


##Barplots
```{r}
label.df <- data.frame(sentiment = c("negemo", "negemo", "posemo", "posemo"),
                       graph = c("Monthly Graph", "Yearly Graph", "Monthly Graph", "Yearly Graph"),
                       quartile = c("Top 25%", "Top 25%", "Bottom 25%", "Bottom 25%"),
                       mean_score = c(0.023, 0.023, 0.039, 0.039))
ns_summary_df %>%
  filter(quartile != "middle") %>%
  group_by(graph, sentiment, quartile) %>%
  summarize(mean_score = mean(score),
            se = sd(score)/sqrt(n())) %>%
  mutate(ymin = mean_score - se,
         ymax = mean_score + se) %>%
  ungroup() %>%
  ggplot(mapping = aes(x = quartile, y = mean_score, fill = quartile)) +
  geom_bar(stat = "identity") +
  geom_errorbar(mapping = aes(ymax = ymax, ymin = ymin)) +
  facet_grid(graph~sentiment, labeller = labeller(sentiment = sent_labs)) +
  labs(x = "Node Strength Quartile", y = "Mean Sentiment Score",
       title = "Node Strength vs. Sentiment Score by Graph Type") +
  geom_text(data = label.df, label = c("***")) +
  guides(fill=FALSE)
```


##Mann-Whitney Tests

###Negative Sentiment vs. Node Strength

####Monthly Graph

```{r}
ns_summary_df %>%
  filter(quartile != "middle", 
         graph == "Monthly Graph",
         sentiment == "negemo") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(score, quartile) %>%
  as.matrix() %>%
  wilcox.test(score ~ quartile, data = .) 
```

####Yearly Graph

```{r}
ns_summary_df %>%
  filter(quartile != "middle", 
         graph == "Yearly Graph",
         sentiment == "negemo") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(score, quartile) %>%
  as.matrix() %>%
  wilcox.test(score ~ quartile, data = .) 
```

###Positive Sentiment vs. Node Strength

####Monthly Graph

```{r}
ns_summary_df %>%
  filter(quartile != "middle", 
         graph == "Monthly Graph",
         sentiment == "posemo") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(score, quartile) %>%
  as.matrix() %>%
  wilcox.test(score ~ quartile, data = .) 
```

####Yearly Graph

```{r}
ns_summary_df %>%
  filter(quartile != "middle", 
         graph == "Yearly Graph",
         sentiment == "posemo") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(score, quartile) %>%
  as.matrix() %>%
  wilcox.test(score ~ quartile, data = .) 
```

#Distribution Summaries

##Distributions of Positive vs. Negative Sentiment
```{r}
df %>%
  select(posemo, negemo) %>%
  gather(category, fraction, everything()) %>%
  ggplot(mapping = aes(x = fraction, fill  = category)) +
  geom_density(alpha = 1/2) +
  scale_fill_discrete(name = "LIWC Category",
                      labels = c("posemo" = "Positive Emotion",
                                 "negemo" = "Negative Emotion")) + 
  labs(x = "Sentiment Score", y = "Density", 
       title = "Sentiment Distribution across Subreddits")
```

Positive sentiment is higher than negative sentiment across subreddits,
on average. 

##Subreddits with Highest Negative Sentiment 
```{r}
df %>% 
  arrange(desc(negemo)) %>%
  slice(1:20) %>%
  ggplot(mapping = aes(x = reorder(subreddit, negemo), y = negemo)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(breaks = seq(0,0.13,0.01), labels = scales::percent) +
  coord_flip() +
  labs(x = "Subreddit", y = "Average Percent of Negative Emotion Words",
       title = "Percent of Negative Emotion Words in Top 20 Subreddits")
```

Subreddits with the highest negative sentiment tend to be related to **Sports**.

##Subreddits with Highest Positive Sentiment 
```{r}
df %>% 
  arrange(desc(posemo)) %>%
  slice(1:20) %>%
  ggplot(mapping = aes(x = reorder(subreddit, posemo), y = posemo)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
  labs(x = "Subreddit", y = "Average Percent of Positive Emotion Words",
       title = "Percent of Positive Emotion Words in Top 20 Subreddits")
```

Subreddits with the highest negative sentiment tend to be **NSFW**. 

##Distributions of Clustering Coefficients by Graph Type

```{r}
df %>%
  select(monthly_clust_coef, yearly_clust_coef, 
         monthly_alt_clust_coef, yearly_alt_clust_coef) %>%
  gather(clust_coef_type, clust_coef, monthly_clust_coef:yearly_alt_clust_coef) %>%
  mutate(graph = ifelse(str_detect(clust_coef_type, "monthly"), "Monthly Graph", "Yearly Graph"),
         clust_coef_type = ifelse(str_detect(clust_coef_type, "alt"), 
                                  "Onnela Coefficient", "Barrat Coefficient")) %>%
  ggplot(mapping = aes(x = clust_coef)) +
  geom_histogram() +
  facet_grid(graph~clust_coef_type, scales = "free") +
  labs(x = "Clustering Coefficient Value", y = "Count",
       title = "Histogram of Clustering Coefficients by Graph Type")
```

##Distributions of Node Strength by Graph Type

```{r}
df %>%
  select(monthly_ns, yearly_ns) %>%
  gather(graph, node_strength, monthly_ns:yearly_ns) %>%
  mutate(graph = str_replace(graph, pattern = "_ns", replacement = ""),
         graph = ifelse(graph == "yearly", "Yearly Graph", "Monthly Graph")) %>%
  ggplot(mapping = aes(x = node_strength)) +
  geom_histogram(binwidth = 0.1) +
  facet_grid(graph~.) +
  labs(x = "Node Strength", y = "Count",
       title = "Histogram of Node Strengths by Graph Type")
```

