---
title: "LIWC Data Analysis 1"
author: "Samuel Hansen"
date: "11/2/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)
```

#Overview

This study examines the relationship between LIWC variables and network 
variables derived from the network containing the top 10% of the edges by 
edge weight. 

```{r}
#Initialize libraries:
library(pvclust)
library(ggrepel)
library(rvest)
library(stringr)
library(GGally)
library(tidyverse)
```

```{r}
# Read in data: 
df <- 
  read_tsv("../../data/liwc_data.tsv", col_names = FALSE) %>%
  plyr::rename(replace = c("X1" = "subreddit", "X2" = "category", "X3" = "fraction")) %>%
  spread(category, fraction) %>%
  # Impute missing values with column medians 
  dmap_at(colnames(.), ~ifelse(is.na(.x), median(.x, na.rm = T), .x)) %>%
  # Merge with graph data  
  left_join(read_tsv("../../data/partial_G_data.tsv") %>% select(-X1), by = "subreddit")
```

#Distributions of Sentiment 

##Distributions of Positive vs. Negative Sentiment
```{r}
df %>%
  select(posemo, negemo) %>%
  gather(category, fraction, everything()) %>%
  ggplot(mapping = aes(x = fraction, fill  = category)) +
  geom_density(alpha = 1/2) +
  scale_x_continuous(labels = scales::percent) +
  scale_fill_discrete(name = "LIWC Category",
                      labels = c("posemo" = "Positive Emotion",
                                 "negemo" = "Negative Emotion")) + 
  labs(x = "% of Word Category in Subreddit", y = "Density", 
       title = "Distribution of % of Positive vs. Negative Words in Subreddits")
```

Positive sentiment is higher than negative sentiment across subreddits,
on average. 

##Subreddits with Highest Negative Sentiment 
```{r}
df %>% 
  arrange(desc(negemo)) %>%
  slice(1:20) %>%
  ggplot(mapping = aes(x = reorder(subreddit, negemo), y = negemo)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(breaks = seq(0,0.13,0.01), labels = scales::percent) +
  coord_flip() +
  labs(x = "Subreddit", y = "Average Percent of Negative Emotions Words",
       title = "Percent of Negative Emotion Words in Top 20 Subreddits")
```

Subreddits with the highest negative sentiment tend to be related to **Sports**.

##Subreddits with Highest Positive Sentiment 
```{r}
df %>% 
  arrange(desc(posemo)) %>%
  slice(1:20) %>%
  ggplot(mapping = aes(x = reorder(subreddit, posemo), y = posemo)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
  labs(x = "Subreddit", y = "Average Percent of Positive Emotions Words",
       title = "Percent of Positive Emotion Words in Top 20 Subreddits")
```

Subreddits with the highest negative sentiment tend to be **NSFW**. 

#Distribution of Network Variables 

##Subreddits with Highest Degree Centrality
```{r}
df %>% 
  arrange(desc(DegCent)) %>%
  slice(1:20) %>%
  ggplot(mapping = aes(x = reorder(subreddit, DegCent), y = DegCent)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = "Subreddit", y = "Degree Centrality",
       title = "Degree Centrality in Top 20 Subreddits")
```

##Subreddits with Highest Closeness Centrality
```{r}
df %>% 
  arrange(desc(CloseCent)) %>%
  slice(1:20) %>%
  ggplot(mapping = aes(x = reorder(subreddit, CloseCent), y = CloseCent)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = "Subreddit", y = "Closeness Centrality",
       title = "Closeness Centrality in Top 20 Subreddits")
```

##Histogram of Unweighted Clustering Coefficients
```{r}
df %>%
  ggplot(mapping = aes(x = ClustCoef)) +
  geom_histogram(binwidth = 0.02) +
  scale_x_continuous(breaks = seq(0,1,0.1)) + 
  labs(x = "Clustering Coefficient", y= "Count", 
       title = "Histogram of Unweighted Clustering Coefficients")
```

#Network Variables vs. Sentiment 

We inspect the pairwise relationships between network variables and 
sentiment scores in the following plot:
```{r}
df %>%
  select(posemo, negemo, DegCent:ClustCoef) %>%
  ggpairs()
```

The relationship between sentiment scores and clustering coefficient
seems to be weak. To take a closer look, the following plots depict the relationship between *unweighted* clustering coefficient and positive and negative sentiment. 
```{r}
sentiment_labs <- c("posemo" = "Positive Words",
                    "negemo" = "Negative Words")
df %>%
  select(posemo, negemo, ClustCoef) %>%
  gather(category, fraction, posemo:negemo) %>%
  ggplot(mapping = aes(x = fraction, y = ClustCoef)) +
  geom_point(alpha = 1/2) +
  scale_x_continuous(labels = scales::percent) +
  scale_y_continuous(limits = c(0,1)) +
  geom_smooth(method = "loess") +
  facet_grid(category~., labeller = labeller(category = sentiment_labs)) +
  labs(x = "% of Word Category in Subreddit", y = "Clustering Coefficient",
       title = "Positive & Negative Sentiment vs. Clustering Coefficient") 
  
```

The straight line of the LOESS smoother indicates the relationship
between sentiment and clustering coefficient is weak. However, we can confirm
this by inspecting the output from regressions of positive and negative 
sentiment onto clustering coefficient. 

###Regression of Positive Sentiment onto Network Variables 
```{r}
(pos.lm.fit <- summary(lm(posemo ~ DegCent + CloseCent + ClustCoef, data = df)))
```

There is a weak, yet highly significant relationship between positive 
sentiment and closeness centrality that implies a 1 unit increase in 
closeness centrality is associated with a 
`r pos.lm.fit$coefficients["CloseCent", "Estimate"]`
unit change in positive sentiment. Further, we also observe a significant
relationship with unweighted clustering coefficient that suggests a 1% increase
in clustering coefficient is associated with a 
`r pos.lm.fit$coefficients["ClustCoef", "Estimate"]`
unit change in positive sentiment. 

###Regression of Negative Sentiment onto Network Variables 
```{r}
(neg.lm.fit <- summary(lm(negemo ~ DegCent + CloseCent + ClustCoef, data = df)))
```

Only degree centrality as a significant positive relationship with negative 
sentiment such that a 1 unit change in degree centrality is associated with
a `r neg.lm.fit$coefficients["DegCent", "Estimate"]` unit change in negative sentiment. 

```{r}
# SCRAPE NSFW SUBREDDITS FROM WEB
# url_data <- "http://redditlist.com/nsfw"
# nsfw_subs <- 
#   url_data %>%
#   read_html() %>% 
#   html_nodes(xpath = '//*[@id="page"]/div[3]') %>% 
#   html_text() %>%
#   str_replace_all("\n", "") %>%
#   str_replace_all("\t", "") %>%
#   str_trim()
#   # str_replace_all("\s", "") %>%
#   str_replace_all("[0-9]+i","") %>%
#   str_extract_all("[a-zA-Z]+") %>%
#   unlist() %>%
#   map(~ifelse(grepl(substring,.x), NA, .x)) %>%
#   unlist() %>%
#   .[!is.na(.)] %>%
#   unique()
#   c()
# 
# #HIERARCHICAL CLUSTERING  
# 
# We perform hierarchical clustering to observe which LIWC features
# are most significantly related to each other. 
# 
# Run hierarchical clustering algorithm: 
# ```{r}
# # clust <- pvclust(liwc_df_wide %>% select(-subreddit))
# clust <- read_rds("../../output/liwc_hierarchical_clust.rds")
# ```
# 
# Plot dendrogram:
# ```{r, fig.height=7, fig.width=10}
# plot(clust)
# pvrect(clust, alpha=0.95)
# ```
# 
# The `sexual` and `negemo` variables are clustered tightly together,
# suggesting a linear relationship may be present. This is visualized below:
# ```{r}
# liwc_df_wide %>%
#   ggplot(mapping = aes(x = sexual, y = posemo)) +
#   geom_point() +
#   scale_x_log10(labels = scales::percent) +
#   scale_y_log10(labels = scales::percent) +
#   geom_smooth(method = "loess")

# KMEANS CLUSTERING 
# library(cluster)
# clusGap(df %>% select(-subreddit), kmeans, 10, B = 100, verbose = interactive())
```
