---
title: "NSFW Analysis"
author: "Samuel Hansen"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE, cache = TRUE)
```

```{r}
# Initialize libraries 
library(rvest)
library(stringr)
library(tidyverse)

# Network data input file
network_file_in <- "data/networkx-weighted-coefficients.tsv"
# Complete network data input file 
complete_network_file_in <- "data/networkx-weighted-coefficients-complete.tsv"
# LIWC data input file 
liwc_file_in <- "data/liwc_data.tsv"
# Node strength input files 
yearly_ns_file_in <- "data/complete_ns.tsv"
monthly_ns_file_in <- "data/monthly_ns.tsv"
```

```{r}
# Read in node strength data 
node_strength_df <-
  
  # Read in yearly graph node strengths 
  read_tsv(yearly_ns_file_in) %>%
  plyr::rename(replace = c("node_strength" = "yearly_ns")) %>% 
  select(-X1) %>%
  
  # Read in monthly graph node strengths 
  left_join(read_tsv(monthly_ns_file_in)) %>%
  plyr::rename(replace = c("node_strength" = "monthly_ns")) %>% 
  select(-X1) %>%
  
  # Gather columns into subreddit, network_type, node_strength 
  gather(network_type, node_strength, yearly_ns:monthly_ns) %>%
  mutate(network_type = str_replace(network_type, 
                                    pattern = "_ns", replacement = "")) 
  
# Read in network data 
network_df <- read_tsv(network_file_in)

# Create data frame 
df <- 
  # Load in complete network data 
  left_join(network_df %>% distinct(subreddit, unique_users), 
            read_tsv(complete_network_file_in) %>% 
              mutate(percent_edges_filtered = "100%")) %>%
  
  # Bind rest of network data 
  bind_rows(network_df) %>% 
  
  # Join LIWC data 
  left_join(
    read_tsv(liwc_file_in, col_names = FALSE) %>%
    plyr::rename(replace = c("X1" = "subreddit", 
                             "X2" = "category", 
                             "X3" = "fraction")) %>%
    spread(category, fraction) %>%
    
    # Impute missing values with column medians 
    dmap_at(colnames(.), ~ifelse(is.na(.x), median(.x, na.rm = T), .x)),
    by = c("subreddit")
  ) %>%
  
  # Join node strength data 
  left_join(node_strength_df)
```


```{r}
# Load list of default subreddits 
default_subs <- 
  read_delim("data/default_subreddits.txt", delim = "\n") %>%
  c()

# Load list of NSFW Subreddits
nsfw_subs <- 
  read_delim("data/nsfw_subreddits.txt", delim = "\n", col_names = FALSE) %>%
  plyr::rename(replace = c("X1" = "nsfw_subreddit")) %>% 
  dmap_at("nsfw_subreddit", str_trim) %>% 
  c()

df <-
  df %>%
  # Label Default subreddits 
  mutate(subreddit_type = ifelse(subreddit %in% default_subs$default_subreddits, 
                                 "Default", "Non-Default"),
         nsfw_status = ifelse(subreddit %in% nsfw_subs$nsfw_subreddit, 
                                 "NSFW", "SFW"))
```

#Networks with Unfiltered Edges 

##Clustering Coefficient vs. Negative Sentiment

###Scatterplot

```{r}
network_labs <- c("yearly" = "Yearly Graph", "monthly" = "Monthly Graph")
df %>%
  filter(percent_edges_filtered == "100%") %>%
  ggplot(mapping = aes(x = clustering_coefficient, y = negemo, color = nsfw_status)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = "loess") +
  # geom_smooth(method = "lm", color = "red") +
  scale_y_log10() + 
  scale_x_log10() +
  facet_grid(network_type~., 
             labeller = labeller(network_type = network_labs)) +
  labs(x = "Clustering Coefficient Value", y = "Negative Sentiment Score",
       title = "Clustering Coefficient vs. Negative Sentiment by Graph Type") +
  scale_color_discrete(name = "Subreddit Type")
```

###Regression 

####Yearly Graph
```{r}
summary(lm(log10(negemo) ~ log10(clustering_coefficient) + nsfw_status, 
                 data = df %>% filter(network_type == "yearly",
                                      percent_edges_filtered == "100%")))
```

####Monthly Graph
```{r}
summary(lm(log10(negemo) ~ log10(clustering_coefficient) + + nsfw_status, 
                 data = df %>% filter(network_type == "monthly",
                                      percent_edges_filtered == "100%")))
```

###Barplot

```{r}
# Compute quartiles of clustering coefficient 
nsfw_clust_summary_df <- 
df %>%
  group_by(network_type, percent_edges_filtered, nsfw_status) %>%
  mutate(quartile = ifelse(clustering_coefficient >= 
                             quantile(clustering_coefficient, 
                                      prob = 0.75, na.rm = T), "Top 25%",
                           ifelse(clustering_coefficient <= 
                                    quantile(clustering_coefficient, 
                                             prob = 0.25, na.rm = T), "Bottom 25%",
                           "middle"))) %>%
  filter(quartile != "middle") %>%
  ungroup()
```

```{r}
label.df <- data.frame(network_type = c("monthly", "yearly", "monthly", "yearly"),
                       nsfw_status = c("NSFW", "NSFW", "SFW", "SFW"),
                       quartile = c("Top 25%", "Top 25%", "Top 25%", "Top 25%"),
                       mean_negemo = c(0.0288, 0.029, 0.0229, 0.0228))

nsfw_clust_summary_df %>%
  filter(percent_edges_filtered == "100%") %>%
  group_by(network_type, quartile, nsfw_status) %>%
  summarize(mean_negemo = mean(negemo),
            se = sd(negemo)/sqrt(n())) %>%
  mutate(ymin = mean_negemo - se,
         ymax = mean_negemo + se) %>%
  ggplot(mapping = aes(x = quartile, y = mean_negemo, fill = quartile)) +
  geom_bar(stat = "identity") +
  geom_errorbar(mapping = aes(ymax = ymax, ymin = ymin)) +
  geom_text(data = label.df, label = c("***", "***", "***", "***")) +
  facet_grid(network_type ~ nsfw_status,
             labeller = labeller(network_type = network_labs)) +
  labs(x = "Clustering Coefficient Quartile", y = "Mean Negative Sentiment Score",
       title = "Clustering Coefficient vs. Negative Sentiment by Graph Type") +
  guides(fill=FALSE)
```

###Mann-Whitney Tests 

####Yearly Graph

#####SFW
```{r}
nsfw_clust_summary_df %>%
  filter(network_type == "yearly", nsfw_status == "SFW",
         percent_edges_filtered == "100%") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(negemo, quartile) %>%
  as.matrix() %>%
  wilcox.test(negemo ~ quartile, data = .) 
```

#####NSFW
```{r}
nsfw_clust_summary_df %>%
  filter(network_type == "yearly", nsfw_status == "NSFW",
         percent_edges_filtered == "100%") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(negemo, quartile) %>%
  as.matrix() %>%
  wilcox.test(negemo ~ quartile, data = .) 
```

####Monthly Graph

#####SFW
```{r}
nsfw_clust_summary_df %>%
  filter(network_type == "monthly", nsfw_status == "SFW",
         percent_edges_filtered == "100%") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(negemo, quartile) %>%
  as.matrix() %>%
  wilcox.test(negemo ~ quartile, data = .) 
```

#####NSFW
```{r}
nsfw_clust_summary_df %>%
  filter(network_type == "monthly", nsfw_status == "NSFW",
         percent_edges_filtered == "100%") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(negemo, quartile) %>%
  as.matrix() %>%
  wilcox.test(negemo ~ quartile, data = .) 
```

##Node Strength vs. Negative Sentiment 

###Scatterplot
```{r}
df %>%
  filter(percent_edges_filtered == "100%") %>%
  ggplot(mapping = aes(x = node_strength, y = negemo, color = nsfw_status)) +
  geom_point(alpha = 0.1) +
  # scale_x_log10() +
  scale_y_log10() +
  geom_smooth(method = "loess") +
  facet_grid(network_type~., labeller = labeller(network_type = network_labs)) +
  labs(x = "Node Strength", y = "Negative Sentiment Score",
       title = "Node Strength vs. Negative Sentiment") +
  scale_color_discrete(name = "Subreddit Type")
```

###Regression

####Yearly Graph
```{r}
summary(lm(log10(negemo) ~ node_strength + nsfw_status, 
                 data = df %>% filter(network_type == "yearly",
                                      percent_edges_filtered == "100%")))
```

A 1 unit change in node strength is associated with a 0.044% change in 
negative sentiment. 
####Monthly Graph
```{r}
summary(lm(log10(negemo) ~ log10(node_strength) + nsfw_status, 
                 data = df %>% filter(network_type == "monthly",
                                      percent_edges_filtered == "100%")))
```

###Barplot

```{r}
# Compute quartiles of node strength
nsfw_ns_summary_df <- 
df %>%
  filter(percent_edges_filtered == "100%") %>%
  group_by(network_type, nsfw_status) %>%
  mutate(quartile = ifelse(node_strength >= 
                             quantile(node_strength, 
                                      prob = 0.75, na.rm = T), "Top 25%",
                           ifelse(node_strength <= 
                                    quantile(node_strength, 
                                             prob = 0.25, na.rm = T), "Bottom 25%",
                           "middle"))) %>%
  filter(quartile != "middle") %>%
  ungroup()
```

```{r}
label.df <- data.frame(network_type = c("monthly", "yearly", "monthly", "yearly"),
                       nsfw_status = c("NSFW", "NSFW", "SFW", "SFW"),
                       quartile = c("Top 25%", "Top 25%", "Top 25%", "Top 25%"),
                       mean_negemo = c(0.0288, 0.0288, 0.0229, 0.0228))

nsfw_ns_summary_df %>%
  group_by(network_type, quartile, nsfw_status) %>%
  summarize(mean_negemo = mean(negemo),
            se = sd(negemo)/sqrt(n())) %>%
  mutate(ymin = mean_negemo - se,
         ymax = mean_negemo + se) %>%
  ggplot(mapping = aes(x = quartile, y = mean_negemo, fill = quartile)) +
  geom_bar(stat = "identity") +
  geom_errorbar(mapping = aes(ymax = ymax, ymin = ymin)) +
  facet_grid(network_type~nsfw_status,
             labeller = labeller(network_type = network_labs)) +
  labs(x = "Node Strength Quartile", y = "Mean Negative Sentiment Score",
       title = "Node Strength vs. Negative Sentiment by Graph Type") +
  geom_text(data = label.df, label = c("***", "***", "***", "***")) +
  guides(fill=FALSE)
```

###Mann-Whitney Tests 

####Yearly Graph

#####SFW
```{r}
nsfw_ns_summary_df %>%
  filter(network_type == "yearly", nsfw_status == "SFW",
         percent_edges_filtered == "100%") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(negemo, quartile) %>%
  as.matrix() %>%
  wilcox.test(negemo ~ quartile, data = .) 
```

#####NSFW
```{r}
nsfw_ns_summary_df %>%
  filter(network_type == "yearly", nsfw_status == "NSFW",
         percent_edges_filtered == "100%") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(negemo, quartile) %>%
  as.matrix() %>%
  wilcox.test(negemo ~ quartile, data = .) 
```

####Monthly Graph

#####SFW
```{r}
nsfw_ns_summary_df %>%
  filter(network_type == "monthly", nsfw_status == "SFW",
         percent_edges_filtered == "100%") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(negemo, quartile) %>%
  as.matrix() %>%
  wilcox.test(negemo ~ quartile, data = .) 
```

#####NSFW
```{r}
nsfw_ns_summary_df %>%
  filter(network_type == "monthly", nsfw_status == "NSFW",
         percent_edges_filtered == "100%") %>%
  mutate(quartile = ifelse(quartile == "Top 25%", 1, 0)) %>%
  ungroup() %>%
  select(negemo, quartile) %>%
  as.matrix() %>%
  wilcox.test(negemo ~ quartile, data = .) 
```

##Subreddit Size vs. Negative Sentiment 

###Scatterplot

```{r}
df %>%
  distinct(subreddit, unique_users, negemo, nsfw_status) %>%
  ggplot(mapping = aes(x = unique_users, y = negemo, color = nsfw_status)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = "loess") +
  scale_x_log10(labels = scales::comma) +
  scale_y_log10() +
  labs(x = "Number of Unique Users", 
       y = "Negative Sentiment Score",
       title = "Subreddit Size vs. Negative Sentiment")+
  scale_color_discrete(name = "Subreddit Type")
```

###Regression
```{r}
summary(lm(log10(negemo) ~ log10(unique_users) + nsfw_status, 
                 data = df %>% distinct(subreddit, unique_users, negemo, nsfw_status)))
```

##Subreddit Size vs. Clustering Coefficient 

###Scatterplot
```{r}
df %>%
  filter(percent_edges_filtered == "100%") %>%
  ggplot(mapping = aes(x = unique_users, y = clustering_coefficient, 
                       color = nsfw_status)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = "loess") +
  scale_x_log10(labels = scales::comma) +
  scale_y_log10() +
  facet_grid(.~network_type, 
             labeller = labeller(network_type = network_labs)) +
  labs(x = "Number of Unique Users", 
       y = "Clustering Coefficient",
       title = "Subreddit Size vs. Clustering Coefficient") +
  scale_color_discrete(name = "Subreddit Type")
```



